---
title: "p8105_hw1_xk2163"
author: "Kang"
date: "2024-09-22"
output: github_document
---

Before doing the HW, I input some need packages.

```{r initial,message=FALSE}
library(tidyverse)
library(ggplot2)
data("penguins", package = "palmerpenguins")
```

# Problem 1

## Get Data Summary

First of all, we need to get the summary information of the whole data.

```{r skim}
skimr::skim(penguins) #get the summary information
```

There are 8 columns, including 3 factor variables and 5 numeric variables.
The factors variables are species, island and sex. The numeric variables are 
bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g and year hist.

## Col & Row

We are going to describe the data. The given dataset has `r nrow(penguins)` rows and `r ncol(penguins)` cols.

```{r}
nrow(penguins)
ncol(penguins)
```

## Taking the average

After that, we are going to take the mean of variable `flipper_length_mm`. And the code are shown below. The average of `flipper_length_mm` is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE) # take the average ignoring the NAs.
```

## Generating the scatter plot

Then, we are going to make a scatter plot. 

```{r}
ggplot(data = penguins,
       aes(x = bill_length_mm,
           y = flipper_length_mm, color = species))+
  geom_point()
ggsave("plot1.jpg")
```

# Problem 2

## Generate the data frame

First, I generated 4 different variables and grouped them into a data frame.

```{r generating a data frame}
set.seed(1)

data_df = 
  data_frame(
  random_samp = rnorm(10),
  logical_vec = random_samp > 0,
  character_vec = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun", "Holiday", "Weekend", "Workday"),
  factor_vec = factor(c("low", "medium", "high", "low", "medium", 
                          "high", "low", "medium", "high", "medium"),
                      levels = c("low","medium","high"))
  )

print(data_df)
```

## Taking the average of all varibales in the dataframe

```{r take the average}
mean(pull(data_df,random_samp))
mean(pull(data_df,logical_vec))
mean(pull(data_df,character_vec))
mean(pull(data_df,factor_vec))
```

Numeric and logical values can be averaged because they have inherent numeric representations. Character and factor data represent categories without numeric meaning, so calculating a mean isn't possible.

## Convert all variables into numeric

```{r}
as.numeric(pull(data_df,random_samp))
as.numeric(pull(data_df,logical_vec))
as.numeric(pull(data_df,character_vec))
as.numeric(pull(data_df,factor_vec))
```

From the above result, we can also find out the reason. However, if we force a numeric forced conversion, factor can still be converted to a numeric variable. We can convert a factor into numeric because, internally, factors are stored as integer codes representing their levels. When converting, R uses these underlying integer codes, but they only indicate category positions, not actual numeric values.
